---
title: "Hidden Markov Model"
author: "Andrew"
date: "12/17/2020"
output:
  bookdown::html_document2:
    toc: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
    pandoc_args: ["--number-offset=2"]
---

This file should be run after the 'Hidden Markov Model.ipynb'.

```{r setup, include=FALSE}
# these options here change the formatting of how comments are rendered
knitr::opts_chunk$set(collapse = TRUE,
                      comment = "#>",
                      results = "hold",
                      fig.show = "hold")

# Clear any existing variables
rm(list = ls())
```

```{r libraries, message=FALSE}
library(scales)
library(cowplot)
library(glue)
library(DescTools)
library(kSamples)
library(ggExtra)
library(broom)
library(latex2exp)
library(tidyverse)
```

```{r}
# Define terms
strategy_names = c('Uniform Guess',
                   'Avoid Direct Contradictions',
                   'Prevalent Digits',
                   'Successful')
strategy_short = c('UG', 'ADC', 'PD', 'S')
response_names = c('In-House', 'Absent', 'Distractor', 'Target')
```

```{r}
# Set ggplot theme
theme_set(theme_light() +
            theme(plot.title = element_text(hjust = 0.5),
                  text = element_text(size=14)))

hues = hue_pal()(4)
colors = c()
colors[[strategy_names[1]]] = hues[4]
colors[[strategy_names[2]]] = hues[3]
colors[[strategy_names[3]]] = hues[1]
colors[[strategy_names[4]]] = hues[2]
colors[[strategy_short[1]]] = hues[4]
colors[[strategy_short[2]]] = hues[3]
colors[[strategy_short[3]]] = hues[1]
colors[[strategy_short[4]]] = hues[2]
colors[[response_names[1]]] = hues[4]
colors[[response_names[2]]] = hues[3]
colors[[response_names[3]]] = hues[1]
colors[[response_names[4]]] = hues[2]

# Disable summarize ungroup messages
options(dplyr.summarise.inform = FALSE)

update_geom_defaults("bar",   list(fill = hues[3]))
```

# Helper functions
```{r}
tidy_ecdf = function(df, colName) {
  x = df %>% 
    pull(!!enquo(colName))
  colName = enquo(colName)
  df = tibble(colName = unique(x),
              cdf = ecdf(x)(colName)) %>%
    arrange(colName) %>% 
    rename(!!quo_name(colName) := colName)
  return (df)
}
```

# Load data

```{r, message=F}
load_tsv = function(filename) {
  df = read_tsv(glue("../data/hmm/solvers/{filename}.tsv")) %>% 
    rbind(read_tsv(glue("../data/hmm/nonsolvers/{filename}.tsv")))
  return (df)
}

df_puzzle = read_tsv("../data/processed/puzzle_data.tsv") %>% 
  mutate(response_type = recode_factor(response_type,
                                       `inhouse` = response_names[1],
                                       `absent` = response_names[2],
                                       `distractor` = response_names[3],
                                       `target` = response_names[4]),
         correct = response_type == response_names[4])
df_subject = read_tsv("../data/processed/subject_data.tsv")

df_agg_p_responses = read_tsv("../data/hmm/solvers/macro_p_response.tsv") %>% 
  mutate(trial = trial + 1,
         response_type = factor(response_names[response_type + 1],
                                response_names))
df_agg_p_strategies = read_tsv("../data/hmm/solvers/macro_p_strategy.tsv") %>% 
  mutate(trial = trial + 1,
         strategy = factor(strategy_names[strategy + 1],
                           strategy_names))

df_p_responses = load_tsv("subject_p_responses") %>% 
  mutate(trial = trial + 1,
         response_type = factor(response_names[response_type + 1],
                                response_names))
df_p_strategies = load_tsv("subject_p_strategies") %>% 
  mutate(trial = trial + 1,
         strategy = factor(strategy_names[strategy + 1],
                           strategy_names))

df_top_paths = load_tsv("top_paths") %>% 
  mutate(trial = trial + 1,
         strategy = factor(strategy_names[strategy + 1],
                           strategy_names))
df_p_top_paths = load_tsv("top_paths_probs")

solver_ids = df_subject %>% 
  filter(solver) %>% 
  pull(subject_id)
```

# Model accuracy
```{r}
df.sim.strategy = read_tsv("../data/hmm/solvers/sim_strategy_accuracy.tsv") %>% 
  mutate(trial = trial + 1,
         strategy = factor(strategy_short[strategy + 1],
                           strategy_short))

# Accuracy by strategy
df.sim.strategy %>% 
  filter(p_actual == 1) %>% 
  group_by(strategy) %>% 
  summarize(accuracy = mean(p_predicted))

df.hs.actual = df.sim.strategy %>% 
  filter(p_actual == 1,
         strategy == 'S') %>% 
  group_by(sim) %>% 
  summarize(hs.start.actual = min(trial))

df.hs.pred = df.sim.strategy %>% 
  filter(strategy == 'S') %>% 
  crossing(threshold = c(.5, .67, .8, .9) %>% round(2)) %>% 
  filter(p_predicted >= threshold) %>% 
  group_by(sim, threshold) %>% 
  summarize(hs.start.pred = min(trial))

df.p.hs = df.hs.actual %>% 
  left_join(df.hs.pred)
```

## P(actual_strat = HS | predicted_strat = HS)

### Optimal threshold

#### Metric: accuracy
```{r}
df.thresholds = df.sim.strategy %>%
  filter(strategy == 'S') %>%
  crossing(threshold = seq(.5, .99, .01) %>% round(2)) %>%
  mutate(predicted = p_predicted >= threshold,
         correct = predicted == p_actual) %>%
  group_by(threshold) %>%
  summarize(accuracy = mean(correct)) %>%
  mutate(method = as.character(threshold)) %>% 
  select(-threshold)

df.thresholds = df.sim.strategy %>% 
  group_by(sim, trial) %>% 
  filter(p_predicted == max(p_predicted)) %>% 
  ungroup() %>% 
  summarize(accuracy = mean(p_actual)) %>% 
  mutate(method = 'max(p)') %>% 
  bind_rows(df.thresholds) %>% 
  arrange(desc(accuracy))

top_threshold = df.thresholds %>% 
  filter(accuracy == max(accuracy)) %>% 
  pull(method) %>% 
  as.numeric()

df.thresholds
```

#### Metric: binary cross entropy
```{r}
binary_cross_entropy = function(p_pred, p_actual) {
  bce = -(p_actual * log(p_pred) + (1 - p_actual) * log(1 - p_pred))
  return (bce)
}

df.p.actual = df.sim.strategy %>%
  filter(strategy == 'S') %>%
  group_by(trial) %>% 
  summarize(p_actual = mean(p_actual))

df.p.pred = df.sim.strategy %>%
  filter(strategy == 'S') %>%
  crossing(threshold = seq(.5, .99, .01) %>% round(2)) %>%
  mutate(predicted = p_predicted >= threshold) %>% 
  group_by(trial, threshold) %>% 
  summarize(p_predicted = mean(predicted)) %>% 
  mutate(method = as.character(threshold)) %>% 
  select(-threshold)

df.p.pred = df.sim.strategy %>% 
  group_by(sim, trial) %>% 
  filter(p_predicted == max(p_predicted)) %>% 
  mutate(pred = strategy == 'S') %>% 
  group_by(trial) %>% 
  summarize(p_predicted = mean(pred)) %>% 
  mutate(method = 'max(p)') %>% 
  bind_rows(df.p.pred)

df.p.pred = df.p.pred %>% 
  left_join(df.p.actual) %>% 
  mutate(bce = map2_dbl(p_predicted, p_actual, binary_cross_entropy)) %>% 
  group_by(method) %>% 
  summarize(bce = sum(bce)) %>% 
  arrange(bce)
```

#### Select top threshold

```{r}
df.thresholds = df.thresholds %>% 
  left_join(df.p.pred) %>% 
  select(method, accuracy, bce)

threshold_bce = df.thresholds %>%
  filter(bce == min(bce)) %>%
  pull(method) %>% 
  as.numeric()

threshold_acc = df.thresholds %>%
  filter(accuracy == max(accuracy)) %>%
  pull(method) %>% 
  as.numeric()
```

### Plot

#### Predictions

```{r}
df = df.sim.strategy %>%
  filter(strategy == 'S') %>%
  group_by(trial) %>%
  summarize(p_hs = mean(p_actual)) %>%
  mutate(method = 'actual')

df = df.sim.strategy %>% 
  filter(strategy == 'S') %>% 
  crossing(threshold = c(threshold_bce,
                         .5, .8)) %>% 
  group_by(trial, threshold) %>% 
  summarize(p_hs = mean(p_predicted >= threshold)) %>% 
  mutate(method = case_when(threshold == threshold_bce ~ glue('{threshold_bce} (optimal)'),
                            TRUE ~ as.character(threshold))) %>% 
  select(-threshold) %>% 
  bind_rows(df) %>% 
  arrange(trial, method)

df %>% 
  ggplot(aes(x = trial, y = p_hs, color = method)) +
  geom_line() +
  geom_point() + 
  coord_cartesian(ylim = c(0, 1)) +
  labs(x = "Trial",
       y = "% of Samples") +
  guides(color = guide_legend(title="Theshold")) +
  theme(legend.position = c(.84, .245),
        legend.box.background = element_rect(colour = "black"),
        text = element_text(size=15)) + 
  ggsave(glue("../figures/practice_phase/p_hs_sim.png"), width=6, height=4)
```

#### Prediction Accuracy

```{r}
df = df.sim.strategy %>% 
  filter(strategy == 'S') %>% 
  crossing(threshold = c(threshold_bce,
                         .5, .8)) %>% 
  filter(p_predicted >= threshold) %>% 
  group_by(trial, threshold) %>% 
  summarize(accuracy = mean(p_actual)) %>% 
  mutate(method = case_when(threshold == threshold_bce ~ glue('{threshold_bce} (optimal)'),
                            TRUE ~ as.character(threshold))) %>%
  select(-threshold) %>% 
  arrange(trial, method)

df %>% 
  ggplot(aes(x = trial, y = accuracy, color = method)) +
  geom_line() +
  geom_point() + 
  labs(x = "Trial",
       y = "Accuracy") +
  guides(color = guide_legend(title="Threshold")) +
  theme(legend.position = c(.84, .21),
        legend.box.background = element_rect(colour = "black"),
        text = element_text(size = 15)) +
  ggsave(glue("../figures/practice_phase/p_hs_accuracy.png"), width=6, height=4)
```

## Predicted xtrial given actual xtrial

```{r}
df.xsim.actual = df.sim.strategy %>% 
  filter(p_actual == 1,
         strategy == 'S') %>% 
  group_by(sim) %>% 
  summarize(actual = min(trial))

df.xsim.pred = df.sim.strategy %>% 
  filter(p_predicted >= .6,
         strategy == 'S') %>% 
  group_by(sim) %>% 
  summarize(predicted = min(trial))

df.xsim.actual %>% 
  left_join(df.xsim.pred) %>% 
  filter(actual %in% c(1, 3, 5, 10)) %>% 
  group_by(actual, predicted) %>% 
  count() %>% 
  group_by(actual) %>% 
  mutate(p = n / sum(n)) %>% 
  ggplot(aes(x = predicted, y = p)) +
  geom_bar(stat = 'identity') +
  labs(x = "Predicted Transition Trial",
       y = "Proportion of Samples") +
  theme(text = element_text(size = 15)) + 
  facet_wrap(vars(actual)) +
  ggsave(glue("../figures/practice_phase/pred_xtrial.png"), width=6, height=4)
```

Create table with AUROC
```{r}
df.xtrials = df.sim.strategy %>% 
  filter(p_actual == 1) %>% 
  group_by(sim, strategy) %>% 
  summarize(xtrial = min(trial)) %>% 
  filter(xtrial > 1) %>% 
  mutate(xtrial = xtrial - .5) %>% 
  rename(xstrategy = strategy)

df = df.sim.strategy %>% 
  crossing(threshold = seq(0, 1, .01) %>% round(2)) %>% 
  mutate(predicted = p_predicted >= threshold) %>% 
  rename(pred_strategy = strategy) %>% 
  inner_join(df.xtrials) %>% 
  mutate(dist_from_xtrial = abs(trial - xtrial) - .5,
         actual = as.logical(p_actual)) %>% 
  select(sim, xstrategy, pred_strategy, threshold, dist_from_xtrial, actual, predicted) %>% 
  arrange(sim, threshold, xstrategy, dist_from_xtrial)

df.tpr = df %>% 
  filter(actual) %>% 
  crossing(dist = 0:23) %>% 
  filter(dist_from_xtrial <= dist) %>% 
  group_by(xstrategy, threshold, dist) %>% 
  summarize(tpr = mean(predicted))

df.fpr = df %>% 
  filter(!actual) %>% 
  crossing(dist = 0:23) %>% 
  filter(dist_from_xtrial <= dist) %>% 
  group_by(xstrategy, threshold, dist) %>% 
  summarize(fpr = mean(predicted))

df.roc = df.tpr %>% 
  left_join(df.fpr)

df.auc = df.roc %>% 
  group_by(xstrategy, dist) %>% 
  summarize(auc = AUC(fpr, tpr))

df.auc %>% 
  filter(dist == 0)
```

```{r}
df.auc %>% 
  mutate(strategy = case_when(xstrategy == 'ADC' ~ 'Avoid Direct Contradictions',
                              xstrategy == 'PD' ~ 'Prevalent Digits',
                              xstrategy == 'S' ~ 'Successful')) %>% 
  ggplot(aes(x = dist, y = auc, color = strategy)) + 
  geom_line() +
  labs(x = "Distance From Transition Trial",
       y = "Area Under ROC") +
  guides(color = guide_legend(title="Transition Strategy")) +
  theme(legend.position = c(.735, .21),
        legend.box.background = element_rect(colour = "black"),
        text = element_text(size = 15)) +
  ggsave(glue("../figures/practice_phase/auc.png"), width=6, height=4)
```

# Aggregate performance plot

## Actual responses

### Solvers

```{r}
df_puzzle %>% 
  filter(subject_id %in% solver_ids,
         phase == 1,
         response_type != 'Target') %>% 
  group_by(trial, response_type) %>% 
  summarize(count = n()) %>%
  mutate(frequency = count / length(solver_ids)) %>% 
  ggplot(aes(x = trial, y = frequency, fill = response_type)) +
  scale_fill_manual(values = colors) +
  geom_bar(stat = "identity") + 
  coord_cartesian(y = c(0, 0.5)) +
  labs(x = "Trial",
       y = "Frequency") +
  guides(fill = guide_legend(title="Response Type")) +
  theme(legend.position = c(.83, .80),
        legend.box.background = element_rect(colour = "black"),
        text = element_text(size = 20),
        legend.title = element_text(size = 15),
        legend.text = element_text(size = 15)) +
  ggsave(glue("../figures/practice_phase/responses_solvers.png"), width=6, height=4)
```

### Solvers

```{r}
df_puzzle %>% 
  mutate(group = ifelse(subject_id %in% solver_ids, 'solver', 'nonsolver'))%>% 
  filter(phase == 1) %>% 
  group_by(group, trial, response_type) %>% 
  summarize(count = n()) %>%
  mutate(frequency = count / sum(count)) %>% 
  filter(response_type != 'Target') %>% 
  ggplot(aes(x = trial, y = frequency, fill = response_type)) +
  scale_fill_manual(values = colors) +
  geom_bar(stat = "identity") + 
  facet_wrap(vars(group)) +
  labs(title = "Participant Responses",
       x = "Trial",
       y = "Frequency") +
  guides(fill = guide_legend(title="Response Type")) +
  theme(legend.position = 'bottom',
        text = element_text(size=15)) +
  ggsave(glue("../figures/practice_phase/responses_all.png"), width=6, height=4)
```

## P(responses) - Macro
```{r}
df_agg_p_responses %>% 
  filter(response_type != 'Target') %>% 
  group_by(trial, response_type) %>% 
  summarize(probability = mean(probability)) %>%
  ggplot(aes(x = trial, y = probability, fill = response_type)) +
  scale_fill_manual(values = colors) +
  geom_bar(stat = "identity") + 
  coord_cartesian(y = c(0, 0.5)) +
  labs(x = "Trial",
       y = "P(Response)") +
  guides(fill = guide_legend(title="Response Type")) +
  theme(legend.box.background = element_rect(colour = "black"),
        legend.position = c(.835, .81),
        text = element_text(size = 20),
        legend.title = element_text(size = 15),
        legend.text = element_text(size = 15)) +
  ggsave(glue("../figures/practice_phase/p_responses.png"), width=6, height=4)
```

## P(strategy) - Macro

```{r}
df_agg_p_strategies %>% 
  group_by(trial, strategy) %>% 
  summarize(probability = mean(probability)) %>%
  ggplot(aes(x = trial, y = probability, fill = strategy)) +
  scale_fill_manual(values = colors) +
  geom_bar(stat = "identity") + 
  labs(x = "Trial",
       y = "P(Strategy)") +
  guides(fill = guide_legend(title="Strategy")) +
  theme(legend.box.background = element_rect(colour = "black"),
        legend.position = c(.645, .28),
        text = element_text(size = 20),
        legend.title = element_text(size = 15),
        legend.text = element_text(size = 15)) +
  ggsave(glue("../figures/practice_phase/p_strategies.png"), width=6, height=4)
```

## % of participants predicted to use HS

```{r}
df = df_p_strategies %>% 
  filter(subject_id %in% solver_ids,
         strategy == 'Successful') %>% 
  crossing(threshold = c(threshold_bce, .5, .667, .8)) %>% 
  mutate(pred_hs = probability >= threshold) %>% 
  group_by(trial, threshold) %>% 
  summarize(p_hs = mean(pred_hs)) %>% 
  mutate(method = ifelse(threshold == threshold_bce,
                         glue('{threshold_bce} (optimal)'),
                         as.character(threshold))) %>% 
  select(-threshold)
```

```{r}
df %>% 
  ggplot(aes(x = trial, y = p_hs, color = method)) +
  geom_line(size=1.25) +
  geom_point(size=2) +
  coord_cartesian(ylim = c(0, 1)) + 
  labs(x = 'Trial',
       y = '% of Participants') +
  guides(color = guide_legend(title="Threshold")) +
  theme(legend.box.background = element_rect(colour = "black"),
        legend.position = c(.82, .24),
        text = element_text(size = 20),
        legend.title = element_text(size = 15),
        legend.text = element_text(size = 15)) +
  ggsave(glue("../figures/practice_phase/p_hs.png"), width=6, height=4)
```

# Individual plots

## P(response)

```{r}
sids = df_p_responses %>% 
  pull(subject_id) %>% 
  unique()

for (i in sids) {
  df_pr = df_p_responses %>% 
    filter(subject_id == i) %>% 
    rename(predicted = response_type)
  df_r = df_puzzle %>% 
    filter(subject_id == i,
           phase == 1) %>%
    mutate(correct = as.numeric(correct)) %>% 
    rename(actual = response_type)
  p = ggplot() +
    geom_bar(aes(x = trial,
                 y = probability,
                 fill = predicted),
             data = df_pr,
             alpha = .5,
             stat = 'identity') +
    geom_point(aes(x = trial,
                   y = correct,
                   color = actual),
               size = 2.5,
               data = df_r) +
    scale_fill_manual(values=colors) +
    scale_color_manual(values=colors) +
    labs(title = glue("P(response | sid={i})"))
  ggsave(glue("../figures/p_response/{i}.png"), plot=p, width=6, height=4)
}
```

## P(strategy)

```{r}
for (i in sids) {
  df = df_p_strategies %>% 
    filter(subject_id == i)
  df = df_puzzle %>% 
    filter(subject_id == i,
           phase == 1) %>% 
    mutate(subject_id = i) %>% 
    merge(df) %>% 
    select(trial, strategy, probability, correct, response_type) %>% 
    mutate(correct = as.numeric(correct))
  p = df  %>% 
    ggplot(aes(x = trial)) +
    geom_bar(aes(y = probability, fill = strategy),
             alpha = .5,
             stat = 'identity') +
    geom_point(aes(y = correct, color = response_type),
               size = 2.5) +
    scale_fill_manual(values=colors) +
    scale_color_manual(values=colors) +
    labs(title = glue("P(strategy | sid={i})"))
  ggsave(glue("../figures/p_strategy/{i}.png"), plot=p, width=6, height=4)
}
```


# Trajectories

## 4 subjects to highlight

```{r}
df_p = df_top_paths %>%
    filter(subject_id == 100) %>% 
    merge(df_p_top_paths) %>% 
    filter(rank < 4) %>% 
    mutate(subject_id = as.factor(subject_id),
           rank = as.factor(rank),
           linesize = 1.5 * (probability ^ .8),
           probability = as.factor(round(probability, 3)),
           accuracy = case_when(strategy == strategy_names[1] ~ 1/9,
                                strategy == strategy_names[2] ~ 1/6,
                                strategy == strategy_names[3] ~ 1/2,
                                strategy == strategy_names[4] ~ 1))
```


```{r}
colors2 = c(colors)
colors2[[response_names[4]]] = 'black'

plot_paths = function(sid, title_label) {
  df_r = df_puzzle %>% 
    filter(phase == 1,
           subject_id == sid)
  
  df_p = df_top_paths %>%
    filter(subject_id == sid) %>% 
    merge(df_p_top_paths) %>% 
    filter(rank < 3) %>% 
    mutate(subject_id = as.factor(subject_id),
           rank = as.factor(rank),
           probability = as.factor(round(probability, 2)),
           accuracy = case_when(strategy == strategy_names[1] ~ 1/9,
                                strategy == strategy_names[2] ~ 1/6,
                                strategy == strategy_names[3] ~ 1/2,
                                strategy == strategy_names[4] ~ 1))
  
  p = ggplot() +
    geom_line(data = df_p,
              aes(x = trial,
                  y = accuracy,
                  color = probability),
              size = 1.25,
              position = position_dodge(width = 0.35)) +
    geom_point(data = df_r,
               aes(x = trial,
                   y = as.numeric(correct),
                   fill = response_type),
               shape = 21,
               stroke = 0,
               size = 2.5,
               show.legend = FALSE) +
    scale_size_identity() + 
    labs(title = glue("{title_label} Subject {sid}"),
         x = "Trial",
         y = "Accuracy") +
    scale_fill_manual(values=colors2) +
    guides(color = guide_legend(title = "Probability",
                                reverse = TRUE),
           fill = guide_legend(reverse=TRUE),
           size = FALSE) +
    theme(text = element_text(size=18),
          legend.position = 'bottom',
          legend.margin=margin(0,0,0,0),
          legend.box.margin=margin(0,0,0,0),
          title = element_text(size = 13)) +
    coord_cartesian(y = c(0, 1))
  
  return (p)
}
```

4 subjects, 2x2
```{r}
p = df_puzzle %>% 
  filter(phase == 1,
         subject_id == 154) %>% 
  ggplot(aes(x = trial, y = correct, fill = response_type)) +
  geom_point(shape = 21) +
  scale_fill_manual(values=colors2) +
  theme(legend.position = 'bottom',
        legend.margin=margin(-0,0,0,0),
        legend.box.margin=margin(0,0,0,0),
        legend.title = element_text(size = 15),
        legend.text = element_text(size = 15)) +
  guides(fill = guide_legend(title = "Response Type"))
legend = get_legend(p)

plot_1 = plot_paths(1, '(a)')
plot_2 = plot_paths(80, '(b)')
plot_3 = plot_paths(81, '(c)')
plot_4 = plot_paths(154, '(d)')

p = ggdraw() +
  draw_plot(plot_1, x = 0, y = 0.5, width = .5, height = .5) +
  draw_plot(plot_2, x = 0.5, y = 0.5, width = .5, height = .5) +
  draw_plot(plot_3, x = 0, y = 0, width = .5, height = .5) +
  draw_plot(plot_4, x = 0.5, y = 0, width = .5, height = .5)

p = ggdraw() + 
  draw_plot(p, x = 0, y = 0.05, width = 1, height = .95) +
  draw_grob(legend, x = 0, y = 0, width = 1, height = .05)

ggsave(glue("../figures/practice_phase/paths.png"), plot=p, width=8, height=8)
```

## All subjects

```{r}
subject_ids = df_subject %>% 
  filter(!excluded) %>% 
  pull(subject_id)

for (sid in subject_ids) {
  p = plot_paths(sid)
  ggsave(glue("../figures/practice_phase_paths/{sid}.png"), plot = p,
         width = 6, height = 4)
}
```

# Discrete vs Gradual Transition Plots

```{r, message=F}
df.xsim = read_tsv("../data/hmm/solvers/sim_results.tsv") %>% 
  rename(sid = sim,
         source = xtype) %>% 
  mutate(response = case_when(response == 0 ~ "In-House",
                              response == 1 ~ "Absent",
                              response == 2 ~ "Distractor",
                              response == 3 ~ "Target"),
         trial = trial + 1)

# First, get subjects data
df.xdata = df_puzzle %>% 
  filter(phase == 1,
         subject_id %in% solver_ids) %>% 
  rename(sid = subject_id) %>% 
  mutate(response = as.character(response_type)) %>% 
  select(sid, trial, response)

# Combine it with P(strategy)
df.xdata = df_p_strategies %>% 
  filter(subject_id %in% solver_ids, 
         strategy == "Hidden Singles") %>% 
  rename(sid = subject_id, 
         p_hs_pred = probability) %>% 
  mutate(p_hs = NA) %>% 
  select(sid, trial, p_hs, p_hs_pred) %>% 
  left_join(df.xdata) %>% 
  mutate(source = 'actual') %>% 
  bind_rows(df.xsim %>% 
              select(source, sid, trial, p_hs, p_hs_pred, response)) %>% 
  select(source, sid, trial, response, p_hs, p_hs_pred)
```


## Plot simulated responses

Sanity check: do the response patterns actually look similar to actual responses?
```{r, fig.height=5, fig.width=9}
df_puzzle %>% 
  filter(subject_id %in% solver_ids,
         phase == 1) %>% 
  select(sid = subject_id, trial, response = response_type) %>% 
  mutate(source = 'actual') %>% 
  bind_rows(df.xdata) %>%
  group_by(source, trial, response) %>% 
  summarize(n = n()) %>% 
  mutate(p = n / sum(n)) %>% 
  ungroup() %>% 
  filter(response != "Target") %>% 
  ggplot(aes(x = trial, y = p, fill = response)) +
  geom_bar(stat = 'identity') +
  facet_grid(cols = vars(source)) +
  labs(x = "Trial",
       y = "P(response)",
       fill = "Response Type") +
  theme(legend.position = "bottom",
        text = element_text(size = 15)) +
  ggsave(glue("../figures/transition_rate/p_responses.png"), width=6, height=4)
```

## Some sample strategies

```{r}
set.seed(2)

df.sim_strats = read_tsv("../data/hmm/solvers/xtype_sim_strategies.tsv") %>% 
  mutate(strategy = strategy_short[strategy+1],
         trial = trial + 1)

sim_ids = sample.int(max(df.sim_strats$sim_id), 4)

df.sim_strats %>% 
  filter(xtype == 'discrete',
         sim_id %in% sim_ids) %>% 
  ggplot(aes(x = trial, y = p, fill = strategy)) +
  scale_fill_manual(values = colors) +
  geom_bar(stat = "identity") + 
  labs(title = "Discrete Transition Samples",
       x = "Trial",
       y = "P(Strategy)") +
  guides(fill = guide_legend(title="Strategy")) +
  theme(legend.position = 'bottom',
        text = element_text(size = 15)) +
  facet_wrap(vars(sim_id), ncol=2) +
  ggsave(glue("../figures/practice_phase/sim_strats_disc.png"), width=6, height=4)

df.sim_strats %>% 
  filter(xtype == 'gradual',
         sim_id %in% sim_ids) %>% 
  ggplot(aes(x = trial, y = p, fill = strategy)) +
  scale_fill_manual(values = colors) +
  geom_bar(stat = "identity") + 
  labs(title = "Incremental Transition Samples",
       x = "Trial",
       y = "P(Strategy)") +
  guides(fill = guide_legend(title="Strategy")) +
  theme(legend.position = 'bottom',
        text = element_text(size = 15)) +
  facet_wrap(vars(sim_id), ncol=2) +
  ggsave(glue("../figures/practice_phase/sim_strats_grad.png"), width=6, height=4)
```

## Dirichlet Distributions
```{r}
df.dirich.samples = read_tsv("../data/hmm/solvers/sim_dirich_samples.tsv") %>% 
  pivot_longer(-c(sim, strategy, target),
               names_to = 'measure',
               values_to = 'probability') %>% 
  mutate(strategy = factor(strategy_short[strategy + 1],
                           strategy_short))

df.dirich.samples %>% 
  filter(measure == 'p_transitions') %>% 
  rename(source = strategy) %>% 
  mutate(destination = factor(strategy_short[target + 1],
                              strategy_short)) %>% 
  ggplot(aes(x = probability)) +
  geom_histogram(mapping = aes(y = stat(density) * .05), binwidth=.05) +
  scale_x_continuous(labels = percent) +
  scale_y_continuous(labels = percent) +
  facet_grid(rows = vars(source),
             cols = vars(destination)) +
  labs(title = "Transition Matrix Distributions",
       x = TeX("P(strategy$_{t+1}$|strategy$_t$)"),
       y = "Density") +
  theme(text = element_text(size = 10)) + 
  ggsave(glue("../figures/transition_rate/sample_transition_matrix.png"), width=6, height=4)


df.dirich.samples %>% 
  filter(measure == 'p_strat_responses') %>% 
  mutate(response = factor(response_names[target + 1],
                           response_names)) %>% 
  ggplot(aes(x = probability)) +
  geom_histogram(mapping = aes(y = stat(density) * .05), binwidth=.05) +
  scale_x_continuous(labels = percent) +
  scale_y_continuous(labels = percent) +
  facet_grid(rows = vars(strategy),
             cols = vars(response)) +
  labs(title = "Response Likelihood Matrix Distributions",
       x = "P(response|strategy)",
       y = "Density") +
  theme(text = element_text(size = 10)) + 
  ggsave(glue("../figures/transition_rate/sample_likelihood_matrix.png"), width=6, height=4)

```

```{r}
df.dirich = read_tsv("../data/hmm/solvers/dirichlet_params.tsv") %>% 
  pivot_longer(-c(strategy, target),
               names_to = 'measure',
               values_to = 'alpha')  %>% 
  mutate(strategy = factor(strategy_names[strategy + 1],
                           strategy_names)) %>% 
  group_by(strategy, measure) %>% 
  mutate(beta = sum(alpha) - alpha) %>% 
  crossing(p = seq(0, 1, .001)) %>% 
  mutate(f = dbeta(p, alpha, beta),
         f = ifelse(is.infinite(f), 1000, f)) %>% 
  select(measure, strategy, target, everything()) %>% 
  arrange(measure, strategy, target)

df.dirich %>% 
  filter(measure == 'p_transitions') %>% 
  mutate(destination = factor(strategy_names[target + 1],
                              strategy_names)) %>% 
  select(source = strategy, destination, p, f) %>% 
  ggplot(aes(x = p, y = f)) +
  geom_line() +
  facet_grid(rows = vars(source),
             cols = vars(destination)) +
  coord_cartesian(ylim = c(0, 15)) +
  labs(title = "Transition Matrix Distributions",
       x = TeX("P(strategy$_{t+1}$|strategy$_t$)"),
       y = "pdf(p)") +
  ggsave(glue("../figures/transition_rate/transition_matrix_dirich.png"), width=6, height=4)

df.dirich %>% 
  filter(measure == 'p_strat_response') %>% 
  mutate(response = factor(response_names[target + 1],
                           response_names)) %>% 
  select(strategy, response, p, f) %>% 
  ggplot(aes(x = p, y = f)) +
  geom_line() +
  facet_grid(rows = vars(strategy),
             cols = vars(response)) +
  coord_cartesian(ylim = c(0, 20)) +
  labs(title = "Response Likelihood Matrix Distributions",
       x = "P(response|strategy)",
       y = "Density") +
  ggsave(glue("../figures/transition_rate/likelihood_matrix_dirich.png"), width=6, height=4)
```
