---
title: "Hidden Markov Model"
author: "Andrew"
date: "12/17/2020"
output:
  bookdown::html_document2:
    toc: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
    pandoc_args: ["--number-offset=2"]
---

This file should be run after the 'Hidden Markov Model.ipynb'.

```{r setup, include=FALSE}
# these options here change the formatting of how comments are rendered
knitr::opts_chunk$set(collapse = TRUE,
                      comment = "#>",
                      results = "hold",
                      fig.show = "hold")

# Clear any existing variables
rm(list = ls())
```

```{r libraries, message=FALSE}
if (!require("cowplot")) install.packages("cowplot")
if (!require("kSamples")) install.packages("kSamples")
if (!require("ggExtra")) install.packages("ggExtra")
if (!require("latex2exp")) install.packages("latex2exp")
if (!require("furrr")) install.packages("furrr")

library(scales)
library(cowplot)
library(glue)
library(DescTools)
library(kSamples)
library(ggExtra)
library(broom)
library(latex2exp)
library(cowplot)
library(ggpubr)
library(furrr)  # parallelization support for map
library(tidyverse)

plan(multisession, workers = 8)  # number of cores to use
```

```{r}
# Define terms
strategy_names = c('Uniform Guess',
                   'Avoid Direct Contradictions',
                   'Prevalent Digits',
                   'Successful')
strategy_short = c('UG', 'ADC', 'PD', 'S')
response_names = c('In-House', 'Absent', 'Distractor', 'Target')
```

```{r}
# Set ggplot theme
theme_set(theme_light() +
            theme(plot.title = element_text(hjust = 0.5),
                  text = element_text(size=14)))

hues = hue_pal()(4)
colors = c()
colors[[strategy_names[1]]] = hues[4]
colors[[strategy_names[2]]] = hues[3]
colors[[strategy_names[3]]] = hues[1]
colors[[strategy_names[4]]] = hues[2]
colors[[strategy_short[1]]] = hues[4]
colors[[strategy_short[2]]] = hues[3]
colors[[strategy_short[3]]] = hues[1]
colors[[strategy_short[4]]] = hues[2]
colors[[response_names[1]]] = hues[4]
colors[[response_names[2]]] = hues[3]
colors[[response_names[3]]] = hues[1]
colors[[response_names[4]]] = hues[2]

# Disable summarize ungroup messages
options(dplyr.summarise.inform = FALSE)
options(tidyverse.quiet = TRUE)

update_geom_defaults("bar",   list(fill = hues[3]))
```

# Helper functions
```{r}
tidy_ecdf = function(df, colName) {
  x = df %>% 
    pull(!!enquo(colName))
  colName = enquo(colName)
  df = tibble(colName = unique(x),
              cdf = ecdf(x)(colName)) %>%
    arrange(colName) %>% 
    rename(!!quo_name(colName) := colName)
  return (df)
}
```

# Load data

```{r}
subj_group = 'solvers'
subj_name = 'Solvers'
# subj_group = 'nonsolvers'
# subj_name = 'Non-Solvers'
```


```{r message=FALSE, results='hide'}
df_subjects = read_tsv("../data/processed/subjects.tsv", show_col_types = FALSE) %>% 
  filter(!excluded) %>% 
  select(-excluded)

df_responses = df_subjects %>% 
  select(subject_id) %>% 
  left_join(read_tsv("../data/processed/trials.tsv", show_col_types = FALSE)) %>% 
  filter(phase == 1) %>% 
  mutate(response_type = recode_factor(response_type,
                                       `inhouse` = response_names[1],
                                       `absent` = response_names[2],
                                       `distractor` = response_names[3],
                                       `target` = response_names[4]),
         correct = response_type == response_names[4]) %>% 
  select(-phase)

df_macro_responses = map_df(c('solvers', 'nonsolvers'),
                            ~ read_tsv(glue("../data/hmm/{.x}/macro_p_response.tsv"), show_col_types = FALSE) %>% 
                              mutate(group = .x)) %>% 
  mutate(trial = trial + 1,
         response_type = factor(response_names[response_type + 1],
                                response_names))
df_macro_strategies = map_df(c('solvers', 'nonsolvers'),
                             ~ read_tsv(glue("../data/hmm/{.x}/macro_p_strategy.tsv"), show_col_types = FALSE) %>% 
                               mutate(group = .x)) %>% 
  mutate(trial = trial + 1,
         strategy = factor(strategy_names[strategy + 1],
                           strategy_names))

df_micro_responses = map_df(c('solvers', 'nonsolvers'),
                            ~ read_tsv(glue("../data/hmm/{.x}/micro_p_response.tsv"), show_col_types = FALSE) %>% 
                              mutate(group = .x)) %>% 
  mutate(trial = trial + 1,
         response_type = factor(response_names[response_type + 1],
                                response_names))

df_micro_strategies = map_df(c('solvers', 'nonsolvers'),
                             ~ read_tsv(glue("../data/hmm/{.x}/micro_p_strategy.tsv"), show_col_types = FALSE) %>% 
                               mutate(group = .x)) %>% 
  mutate(trial = trial + 1,
         strategy = factor(strategy_names[strategy + 1],
                           strategy_names))

df_top_paths = map_df(c('solvers', 'nonsolvers'),
                      ~ read_tsv(glue("../data/hmm/{.x}/top_paths.tsv"), show_col_types = FALSE) %>% 
                        mutate(group = .x)) %>% 
  mutate(trial = trial + 1,
         strategy = factor(strategy_names[strategy + 1],
                           strategy_names))
df_p_top_paths = map_df(c('solvers', 'nonsolvers'),
                        ~ read_tsv(glue("../data/hmm/{.x}/top_paths_probs.tsv"), show_col_types = FALSE) %>% 
                          mutate(group = .x))
```

## Wrangling

### df_cum_pstrat
```{r}
df_cum_pstrat = df_micro_strategies %>% 
  complete(subject_id, trial, strategy, fill = list(probability = 0)) %>%
  arrange(subject_id, trial, desc(strategy)) %>% 
  group_by(subject_id, trial) %>% 
  mutate(probability = cumsum(probability)) %>% 
  select(-group) %>% 
  ungroup()
```

### df_transitions
```{r}
df_transitions = df_cum_pstrat %>% 
  group_by(subject_id, strategy) %>% 
  filter(probability >= .5) %>% 
  filter(trial == min(trial)) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(subject_id, xtrial=trial, strategy)
```



# Strategy numbers

## P(strategy) using Macro
```{r}
df_macro_strategies %>% 
  filter(strategy == 'Successful') %>% 
  mutate(probability = 100 * round(probability, 3))
```

## P(strategy) using Micro
```{r}
df_thresholds %>% 
  left_join(df_micro_strategies) %>% 
  group_by(group, trial, strategy) %>% 
  summarize(proportion = mean(probability >= threshold))
```


```{r}
df_subjects %>% 
  select(subject_id, solver, p2_accuracy) %>% 
  left_join(df_micro_strategies) %>% 
  left_join(df_thresholds)
```



# Phase 1 Main Plots

## Actual incorrect responses
```{r}
plot = df_responses %>% 
  filter(response_type != 'Target') %>% 
  group_by(trial, response_type) %>% 
  summarize(count = n()) %>%
  mutate(frequency = count / nrow(df_subjects)) %>% 
  ggplot(aes(x = trial, y = frequency, fill = response_type)) +
  scale_fill_manual(values = colors) +
  geom_bar(stat = "identity") + 
  coord_cartesian(y = c(0, .5)) + # for solvers
  # coord_cartesian(y = c(0, .7)) + # for nonsolvers
  scale_x_continuous(expand = c(0.008, 0.008)) +
  scale_y_continuous(expand = c(0.005, 0.005),
                     labels = scales::percent) +
  labs(x = "Trial",
       y = "Frequency") +
  guides(fill = guide_legend(title="Response Type", ncol=2)) +
  theme(text = element_text(size = 20))

legend = get_legend(plot) %>% 
  as_ggplot()
ggsave(glue("../figures/practice_phase/legend_responses.png"), width = 6, height = 1,
       bg = 'white')

plot + rremove('legend')
ggsave(glue("../figures/practice_phase/{subj_group}/responses.png"), width=6, height=4)
```

## Modeled incorrect responses
```{r}
df_macro_responses %>% 
  filter(response_type != 'Target') %>% 
  group_by(trial, response_type) %>% 
  summarize(probability = mean(probability)) %>%
  ggplot(aes(x = trial, y = probability, fill = response_type)) +
  scale_fill_manual(values = colors) +
  geom_bar(stat = "identity") + 
  coord_cartesian(y = c(0, 0.5)) + # for solvers
  # coord_cartesian(y = c(0, .7)) + # for nonsolvers
  scale_x_continuous(expand = c(0.008, 0.008)) +
  scale_y_continuous(expand = c(0.005, 0.005),
                     labels = scales::percent) +
  labs(x = "Trial",
       y = "P(Response)") +
  theme(legend.position = 'none',
        text = element_text(size = 20))
ggsave(glue("../figures/practice_phase/{subj_group}/p_responses.png"), width=6, height=4)
```
## P(strategy) - Macro

```{r}
subj_group = 'solvers'

plot = df_macro_strategies %>% 
  filter(group == subj_group) %>% 
  group_by(trial, strategy) %>% 
  summarize(probability = mean(probability)) %>%
  ggplot(aes(x = trial, y = probability, fill = strategy)) +
  scale_fill_manual(values = colors) +
  geom_bar(stat = "identity") + 
  labs(x = "Trial",
       y = "P(Strategy)") +
  guides(fill = guide_legend(title="Strategy", ncol = 2)) +
  scale_x_continuous(expand = c(0.01, 0.01)) +
  scale_y_continuous(expand = c(0.025, 0.025),
                     labels = scales::percent) +
  theme(text = element_text(size = 20))

legend = get_legend(plot) %>% 
  as_ggplot()
ggsave(glue("../figures/practice_phase/legend_strategies.png"), width = 6, height = 1,
       bg = 'white')

plot + rremove('legend')
ggsave(glue("../figures/practice_phase/{subj_group}/p_strategies_macro.png"), width=6, height=4)
```

## P(strategy) - Micro

```{r}
subj_group = 'solvers'

df_cum_pstrat %>%
  left_join(df_subjects) %>%
  filter(solver == (subj_group == 'solvers')) %>%
  select(subject_id, trial, strategy, probability) %>%
  complete(subject_id, trial, strategy, fill = list(probability = 0)) %>%
  arrange(subject_id, trial, desc(strategy)) %>%
  group_by(subject_id, trial) %>%
  mutate(probability = cumsum(probability)) %>%
  filter(probability >= .5) %>%
  slice(1) %>%
  group_by(trial, strategy) %>% 
  summarize(n = n()) %>% 
  mutate(f = n / sum(n)) %>% 
  ggplot(aes(x = trial, y = f, fill = strategy)) +
  geom_bar(stat = 'identity', show.legend = FALSE) +
  coord_cartesian(ylim = c(0, 1)) +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = colors) +
  # scale_fill_manual(name="", values=c("#29BFC2", "#F47571", "#7DB022")) +
  labs(x = 'Trial', y = "% of Participants") +
  scale_x_continuous(expand = c(0.01, 0.01)) +
  scale_y_continuous(expand = c(0.025, 0.025),
                     labels = scales::percent) +
  theme(text = element_text(size = 20))

ggsave(glue("../figures/practice_phase/{subj_group}/p_strategies_micro.png"), width=6, height=4)
```

### Plot transition trial vs. p2_accuracy
```{r}
df_transitions %>% 
  filter(strategy == 'Successful') %>% 
  group_by(subject_id) %>% 
  summarize(xtrial = min(xtrial)) %>% 
  left_join(df_subjects) %>% 
  group_by(xtrial, p2_accuracy, solver) %>% 
  count() %>% 
  mutate(solver = ifelse(solver, 'Solver', 'Non-Solver') %>% 
           factor(c('Solver', 'Non-Solver'))) %>% 
  ggplot(aes(x = xtrial, y = p2_accuracy, color = solver, size = n, shape = solver)) +
  geom_point(alpha = .7) +
  scale_color_manual(values=c("#29BFC2", "#F47571"))

ggsave("../figures/temp/xtrial_p2acc.png", width=6, height=4)
```

What do the late solvers' practice phase profiles look like?
```{r}
df_transitions %>% 
  filter(strategy == 'Successful') %>% 
  left_join(df_subjects) %>% 
  select(subject_id, xtrial, p2_accuracy) %>% 
  arrange(desc(xtrial), p2_accuracy)
```



# Individual plots

## P(response)

```{r}
sids = df_p_responses %>% 
  pull(subject_id) %>% 
  unique()

i = 1

for (i in sids) {
  df_pr = df_p_responses %>% 
    filter(subject_id == i) %>% 
    rename(predicted = response_type)
  df_r = df_puzzle %>% 
    filter(subject_id == i,
           phase == 1) %>%
    mutate(correct = as.numeric(correct)) %>% 
    rename(actual = response_type)
  p = ggplot() +
    geom_bar(aes(x = trial,
                 y = probability,
                 fill = predicted),
             data = df_pr,
             alpha = .5,
             stat = 'identity') +
    geom_point(aes(x = trial,
                   y = correct,
                   color = actual),
               size = 2.5,
               data = df_r) +
    scale_fill_manual(values=colors) +
    scale_color_manual(values=colors) +
    labs(title = glue("P(response | sid={i})"))
  ggsave(glue("../figures/p_response/{i}.png"), plot=p, width=6, height=4)
}
```

## P(strategy)

```{r}
for (sid in df_subjects$subject_id) {
  p = ggplot() +
    geom_bar(aes(x = trial, y = probability, fill = strategy),
             data = df_micro_strategies %>% 
               filter(subject_id == sid),
             alpha = .5,
             stat = 'identity',
             show.legend = FALSE) +
    geom_point(aes(x = trial, y = as.numeric(correct), color = response_type),
               data = df_responses %>% 
                 filter(subject_id == sid),
               size = 2.5,
               show.legend = FALSE) +
    scale_fill_manual(values=colors) +
    scale_color_manual(values=colors) +
    labs(title = glue("Subject {sid}"),
         x = 'Trial',
         y = 'P(strategy)') +
    theme(legend.position = 'bottom')
  
  ggsave(glue("../figures/practice_phase/strategies/{sid}.png"), plot=p, width=6, height=4)
}
```

# Trajectories

## 4 subjects to highlight

```{r}
df_p = df_top_paths %>%
  filter(subject_id == 100) %>% 
  merge(df_p_top_paths) %>% 
  filter(rank < 4) %>% 
  mutate(subject_id = as.factor(subject_id),
         rank = as.factor(rank),
         linesize = 1.5 * (probability ^ .8),
         probability = as.factor(round(probability, 3)),
         accuracy = case_when(strategy == strategy_names[1] ~ 1/9,
                              strategy == strategy_names[2] ~ 1/6,
                              strategy == strategy_names[3] ~ 1/2,
                              strategy == strategy_names[4] ~ 1))
```


```{r}
colors2 = c(colors)
colors2[[response_names[4]]] = 'black'

sid = 81
plot_paths = function(sid) {
  df_r = df_responses %>% 
    filter(subject_id == sid)
  
  df_p = df_top_paths %>%
    filter(subject_id == sid) %>% 
    merge(df_p_top_paths) %>% 
    filter(rank < 3) %>% 
    arrange(desc(probability)) %>% 
    mutate(subject_id = factor(subject_id),
           # rank = factor(rank),
           probabability = glue("{100 * round(probability, 2)}%"),
           probability = factor(probabability,
                                rev(unique(probabability))),
           accuracy = case_when(strategy == strategy_names[1] ~ 1/9,
                                strategy == strategy_names[2] ~ 1/6,
                                strategy == strategy_names[3] ~ 1/2,
                                strategy == strategy_names[4] ~ 1))
  
  p = ggplot() +
    geom_line(data = df_p,
              aes(x = trial,
                  y = accuracy,
                  color = probability),
              size = 1.25,
              # show.legend = FALSE,
              position = position_dodge(width = 0.35)) +
    geom_point(data = df_r,
               aes(x = trial,
                   y = as.numeric(correct),
                   fill = response_type),
               shape = 21,
               stroke = 0,
               size = 2.5,
               show.legend = FALSE
               ) +
    scale_size_identity() + 
    labs(
      # title = glue("Subject {sid}"),
         x = "Trial",
         y = "Accuracy") +
    # scale_color_discrete(labels = scales::percent) +
    # scale_x_continuous(labels = seq(5, 25, 5)) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(values=colors2) +
    guides(color = guide_legend(title = "Probability",
                                reverse = TRUE),
           fill = guide_legend(title = "",
                               reverse=TRUE),
           size = FALSE) +
    theme(text = element_text(size=18),
          legend.position = 'bottom',
          legend.margin=margin(0,0,0,0),
          legend.box.margin=margin(0,0,0,0),
          title = element_text(size = 13)) +
    coord_cartesian(y = c(0, 1))
  
  return (p)
}
```

```{r}
for (sid in c(1, 80, 81, 154)) {
  plot = plot_paths(sid)
  ggsave(glue("../figures/paths_selected/{sid}.png"), width = 6, height = 4, 
         scale = .8,
         bg = 'white')
}



legend = get_legend(plot) %>% 
  as_ggplot()
ggsave(glue("../figures/paths_selected/legend_responses.png"), width = 6, height = 1,
       bg = 'white')

plot + rremove('legend')
plot
```


4 subjects, 2x2
```{r}
p = df_puzzle %>% 
  filter(phase == 1,
         subject_id == 154) %>% 
  ggplot(aes(x = trial, y = correct, fill = response_type)) +
  geom_point(shape = 21) +
  scale_fill_manual(values=colors2) +
  theme(legend.position = 'bottom',
        legend.margin=margin(-0,0,0,0),
        legend.box.margin=margin(0,0,0,0),
        legend.title = element_text(size = 15),
        legend.text = element_text(size = 15)) +
  guides(fill = guide_legend(title = "Response Type"))
legend = get_legend(p)

plot_1 = plot_paths(1, '(a)')
plot_2 = plot_paths(80, '(b)')
plot_3 = plot_paths(81, '(c)')
plot_4 = plot_paths(154, '(d)')

p = ggdraw() +
  draw_plot(plot_1, x = 0, y = 0.5, width = .5, height = .5) +
  draw_plot(plot_2, x = 0.5, y = 0.5, width = .5, height = .5) +
  draw_plot(plot_3, x = 0, y = 0, width = .5, height = .5) +
  draw_plot(plot_4, x = 0.5, y = 0, width = .5, height = .5)

p = ggdraw() + 
  draw_plot(p, x = 0, y = 0.05, width = 1, height = .95) +
  draw_grob(legend, x = 0, y = 0, width = 1, height = .05)

ggsave(glue("../figures/practice_phase/paths.png"), plot=p, width=8, height=8)
```

## All subjects

```{r}
for (sid in df_subjects$subject_id) {
  p = plot_paths(sid)
  ggsave(glue("../figures/practice_phase_paths/{sid}.png"), plot = p,
         width = 6, height = 4)
}
```

# Discrete vs Gradual Transition Plots

```{r, message=F}
df.xsim = read_tsv("../data/hmm/solvers/sim_results.tsv") %>% 
  rename(sid = sim,
         source = xtype) %>% 
  mutate(response = case_when(response == 0 ~ "In-House",
                              response == 1 ~ "Absent",
                              response == 2 ~ "Distractor",
                              response == 3 ~ "Target"),
         trial = trial + 1)

# First, get subjects data
df.xdata = df_puzzle %>% 
  filter(phase == 1,
         subject_id %in% solver_ids) %>% 
  rename(sid = subject_id) %>% 
  mutate(response = as.character(response_type)) %>% 
  select(sid, trial, response)

# Combine it with P(strategy)
df.xdata = df_p_strategies %>% 
  filter(subject_id %in% solver_ids, 
         strategy == "Hidden Singles") %>% 
  rename(sid = subject_id, 
         p_hs_pred = probability) %>% 
  mutate(p_hs = NA) %>% 
  select(sid, trial, p_hs, p_hs_pred) %>% 
  left_join(df.xdata) %>% 
  mutate(source = 'actual') %>% 
  bind_rows(df.xsim %>% 
              select(source, sid, trial, p_hs, p_hs_pred, response)) %>% 
  select(source, sid, trial, response, p_hs, p_hs_pred)
```


## Plot simulated responses

Sanity check: do the response patterns actually look similar to actual responses?
```{r, fig.height=5, fig.width=9}
df_puzzle %>% 
  filter(subject_id %in% solver_ids,
         phase == 1) %>% 
  select(sid = subject_id, trial, response = response_type) %>% 
  mutate(source = 'actual') %>% 
  bind_rows(df.xdata) %>%
  group_by(source, trial, response) %>% 
  summarize(n = n()) %>% 
  mutate(p = n / sum(n)) %>% 
  ungroup() %>% 
  filter(response != "Target") %>% 
  ggplot(aes(x = trial, y = p, fill = response)) +
  geom_bar(stat = 'identity') +
  facet_grid(cols = vars(source)) +
  labs(x = "Trial",
       y = "P(response)",
       fill = "Response Type") +
  theme(legend.position = "bottom",
        text = element_text(size = 15)) +
  ggsave(glue("../figures/transition_rate/p_responses.png"), width=6, height=4)
```

## Some sample strategies

```{r}
set.seed(2)

df.sim_strats = read_tsv("../data/hmm/solvers/xtype_sim_strategies.tsv") %>% 
  mutate(strategy = strategy_short[strategy+1],
         trial = trial + 1)

sim_ids = sample.int(max(df.sim_strats$sim_id), 4)

df.sim_strats %>% 
  filter(xtype == 'discrete',
         sim_id %in% sim_ids) %>% 
  ggplot(aes(x = trial, y = p, fill = strategy)) +
  scale_fill_manual(values = colors) +
  geom_bar(stat = "identity") + 
  labs(title = "Discrete Transition Samples",
       x = "Trial",
       y = "P(Strategy)") +
  guides(fill = guide_legend(title="Strategy")) +
  theme(legend.position = 'bottom',
        text = element_text(size = 15)) +
  facet_wrap(vars(sim_id), ncol=2) +
  ggsave(glue("../figures/practice_phase/sim_strats_disc.png"), width=6, height=4)

df.sim_strats %>% 
  filter(xtype == 'gradual',
         sim_id %in% sim_ids) %>% 
  ggplot(aes(x = trial, y = p, fill = strategy)) +
  scale_fill_manual(values = colors) +
  geom_bar(stat = "identity") + 
  labs(title = "Incremental Transition Samples",
       x = "Trial",
       y = "P(Strategy)") +
  guides(fill = guide_legend(title="Strategy")) +
  theme(legend.position = 'bottom',
        text = element_text(size = 15)) +
  facet_wrap(vars(sim_id), ncol=2) +
  ggsave(glue("../figures/practice_phase/sim_strats_grad.png"), width=6, height=4)
```

## Dirichlet Distributions
```{r}
df.dirich.samples = read_tsv("../data/hmm/solvers/sim_dirich_samples.tsv") %>% 
  pivot_longer(-c(sim, strategy, target),
               names_to = 'measure',
               values_to = 'probability') %>% 
  mutate(strategy = factor(strategy_short[strategy + 1],
                           strategy_short))

df.dirich.samples %>% 
  filter(measure == 'p_transitions') %>% 
  rename(source = strategy) %>% 
  mutate(destination = factor(strategy_short[target + 1],
                              strategy_short)) %>% 
  ggplot(aes(x = probability)) +
  geom_histogram(mapping = aes(y = stat(density) * .05), binwidth=.05) +
  scale_x_continuous(labels = percent) +
  scale_y_continuous(labels = percent) +
  facet_grid(rows = vars(source),
             cols = vars(destination)) +
  labs(title = "Transition Matrix Distributions",
       x = TeX("P(strategy$_{t+1}$|strategy$_t$)"),
       y = "Density") +
  theme(text = element_text(size = 10)) + 
  ggsave(glue("../figures/transition_rate/sample_transition_matrix.png"), width=6, height=4)


df.dirich.samples %>% 
  filter(measure == 'p_strat_responses') %>% 
  mutate(response = factor(response_names[target + 1],
                           response_names)) %>% 
  ggplot(aes(x = probability)) +
  geom_histogram(mapping = aes(y = stat(density) * .05), binwidth=.05) +
  scale_x_continuous(labels = percent) +
  scale_y_continuous(labels = percent) +
  facet_grid(rows = vars(strategy),
             cols = vars(response)) +
  labs(title = "Response Likelihood Matrix Distributions",
       x = "P(response|strategy)",
       y = "Density") +
  theme(text = element_text(size = 10)) + 
  ggsave(glue("../figures/transition_rate/sample_likelihood_matrix.png"), width=6, height=4)

```

```{r}
df.dirich = read_tsv("../data/hmm/solvers/dirichlet_params.tsv") %>% 
  pivot_longer(-c(strategy, target),
               names_to = 'measure',
               values_to = 'alpha')  %>% 
  mutate(strategy = factor(strategy_names[strategy + 1],
                           strategy_names)) %>% 
  group_by(strategy, measure) %>% 
  mutate(beta = sum(alpha) - alpha) %>% 
  crossing(p = seq(0, 1, .001)) %>% 
  mutate(f = dbeta(p, alpha, beta),
         f = ifelse(is.infinite(f), 1000, f)) %>% 
  select(measure, strategy, target, everything()) %>% 
  arrange(measure, strategy, target)

df.dirich %>% 
  filter(measure == 'p_transitions') %>% 
  mutate(destination = factor(strategy_names[target + 1],
                              strategy_names)) %>% 
  select(source = strategy, destination, p, f) %>% 
  ggplot(aes(x = p, y = f)) +
  geom_line() +
  facet_grid(rows = vars(source),
             cols = vars(destination)) +
  coord_cartesian(ylim = c(0, 15)) +
  labs(title = "Transition Matrix Distributions",
       x = TeX("P(strategy$_{t+1}$|strategy$_t$)"),
       y = "pdf(p)") +
  ggsave(glue("../figures/transition_rate/transition_matrix_dirich.png"), width=6, height=4)

df.dirich %>% 
  filter(measure == 'p_strat_response') %>% 
  mutate(response = factor(response_names[target + 1],
                           response_names)) %>% 
  select(strategy, response, p, f) %>% 
  ggplot(aes(x = p, y = f)) +
  geom_line() +
  facet_grid(rows = vars(strategy),
             cols = vars(response)) +
  coord_cartesian(ylim = c(0, 20)) +
  labs(title = "Response Likelihood Matrix Distributions",
       x = "P(response|strategy)",
       y = "Density") +
  ggsave(glue("../figures/transition_rate/likelihood_matrix_dirich.png"), width=6, height=4)
```

# Blah

```{r}
library(gtools)
rdirichlet(1000, c(0.6594, 1.7297, 2.65, 2.786)) %>% 
  as_tibble() %>% 
  mutate(sid = 1:n()) %>% 
  pivot_longer(starts_with('V')) %>% 
  ggplot(aes(x = value)) +
  facet_wrap(~name) +
  geom_density()
```


